Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-03-22 main.tex
added M-M NASA grant number
Update on Overleaf.

These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work. {\bf We have compared our cooling curves to those used in \citep{Hu2017} (C. Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.}

@@

Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and He from the UV background. This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations. In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
%mm3 
    {\bf [Is there any treatment in the model of the visible light radiation field, which is sufficient to destroy H$^-$?]}

@@

\section*{Acknowledgments:} 
We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. C\^ot\'e, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise. A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was funded by NASA 
%mm3 [have to scare up the number still]
We gratefully recognize computational
resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

>>>>

These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work. We have compared our cooling curves to those used in \citep{Hu2017} (C. Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.

@@

Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and H from the UV background. This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations. In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model. Although we ignore the visible component of our ISRF, capable of destroying H$^{-}$, this is included from the UV background.

@@

\section*{Acknowledgments:} 
We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. C\^ot\'e, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise. A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was partly funded by NASA  grant NNX14AP27G. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.
